R Notebook

### 2018-05-08 analysis/final_analysis.Rmd

@@

dodge <- position_dodge(width=0.9)
d.onDistractor %>%
  group_by(condition, trialType) %>%
  tidyboot_mean(column = hovered) %>%
  ggplot(aes(x = condition, y=empirical_stat, fill = trialType)) +
    geom_bar(stat = 'identity', position = dodge, alpha =.5) +
    geom_errorbar(aes(ymax = ci_upper, ymin = ci_lower), width = 0, position = dodge) +
    theme_few() +
    ylab('% trials hovering over distractor') +
    scale_fill_colorblind()+
    theme(aspect.ratio = 0.5)

ggsave('../writing/journal_manuscript/figures//hoverOverDistractor.pdf', height = 3, width = 6)
```

@@

```{r}
refs <- read_csv('../data/final/experiment1/refExpressions.csv')
scripted <- data.frame(objectSet = c(1,2,3,4,5,6,7,8), 
                       m = c('glasses', 'bottom block', 'tape', 'large measuring cup', 'brush', 'eraser', 'small candle', 'mouse'),
                       numRawWords = c(1,2,1,3,1,1,2,1))
refs %>% 
  mutate(numRawWords = str_count(text, "\\S+")) %>%
  group_by(objectSet) %>%
  tidyboot_mean(numRawWords) %>%
  left_join(scripted)
```

>>>>

## Test error homogeneity

```{r}
errorRates = critTrials %>% 
  mutate(error = 1 - correct) %>%
  group_by(objectSet, condition, targetObject) %>%
  summarize(errors = sum(error), nonerrors = length(error) - errors) %>%
  ungroup()

scriptedErrors <- errorRates %>% 
  filter(condition == 'scripted') %>%
  select(errors, nonerrors)
chisq.test(as.matrix(rbind(scriptedErrors$errors, scriptedErrors$nonerrors)), simulate.p.value = T)

unscriptedErrors <- errorRates %>% 
  filter(condition == 'unscripted') %>%
  select(errors, nonerrors)
chisq.test(as.matrix(rbind(unscriptedErrors$errors, unscriptedErrors$nonerrors)), simulate.p.value = T)
```

@@

dodge <- position_dodge(width=0.9)
d.onDistractor %>%
  group_by(condition, trialType) %>%
  tidyboot_mean(column = hovered) %>%
  mutate(trial = ifelse(trialType == 'base', 'baseline', 'experimental')) %>%
  ggplot(aes(x = condition, y=empirical_stat, fill = condition, group = trial)) +
    geom_bar(aes(alpha = trial), stat = 'identity', position = dodge) +
    geom_errorbar(aes(ymax = ci_upper, ymin = ci_lower), width = 0, position = dodge) +
    theme_few() +
    scale_alpha_manual(values=c(.25, .75)) +
    ylab('% trials hovering over distractor') +
    scale_fill_colorblind()+
    guides(fill='none') +
    theme(aspect.ratio = 1, legend.position = 'top')

ggsave('../writing/journal_manuscript/figures/hoverOverDistractor.pdf', height = 3, width = 3)
```

@@

```{r}
scripted_refs <- c('glasses', 'bottom block', 'tape', 'large measuring cup', 'brush', 'eraser', 'small candle', 'mouse')
standardized_refs <- read_csv('../data/final/experiment1/refExpressions_standardized.csv')
length(unique(c(standardized_refs$text, scripted_refs)))
unscripted_refs <- read_csv('../data/final/experiment1/refExpressions.csv')
scripted.df <- data.frame(objectSet = c(1,2,3,4,5,6,7,8), m = scripted_refs, numRawWords = c(1,2,1,3,1,1,2,1))
refs %>% 
  mutate(numRawWords = str_count(text, "\\S+")) %>%
  group_by(objectSet) %>%
  tidyboot_mean(numRawWords) %>%
  left_join(scripted)
```
